Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-10 analysis/paper/paper.Rmd
add label and other effects to network plot
increase the prior number for gwesp to 5 and the gof improves a bit
add a reference and minor update

The burial data we analyzed in this paper are collected from the upper component of Kiwulan site, an Iron Age settlement site (AD1350-AD1950) located in northeastern Taiwan which experienced the European colonial impacts in the 17th century and the large wave of Chinese immigrants in the 19th century. The excavation revealed abundant pottery sherds, imported ceramics and stonewares, wooden artifacts, stone tools, metal artifacts, imported glass beads and agates beads, and pipes [@Chen2007]. In addition to these artifacts, 90 burials, hundreds of middens, storage pits, and postholes with in-situ posts were also excavated. The burials were mostly located in the AD section, which is the largest open area at Kiwulan site that provides continuous stratigraphic sections suitable for comparison. Those burials are oriented in an east-west direction located on the north side of the house structures indicated by postholes and in-situ wooden posts. Previous research indicates the presence of economic inequality between burials, but there is debate about whether these represent an egalitarian or stratified society [@Cheng2008; @Hsieh2012]. @Cheng2008 interprets the unequal distribution of prestige materials, such as the golden beads, between burials, as evidence for hierarchy. However, @Hsieh2012 suggests a relatively egalitarian form from the comparative analysis of frequency and proportion of burial goods. She finds that the rich burials were usually associated with elders, which might indicate achieved, rather than inherited, status. The use of prestige goods in burials might be traced back before the European arrival according to historical records from Spanish and Chinese [@Borao2009; Li and Wu 2006). Analysing burial data will give an insight into the social reactions of Kiwulan residents and provide a way to examine and explain the changes in social inequality at Kiwulan before and after European contact.

@@

The archaeological sites in northeastern Taiwan show some evidence of accumulation of imported prestige goods in burials (Chen 2005; Cheng 2008), which might indicate the pursuit of prestige or wealth. In addition to prestige, European colonial powers could have provided military support to indigenous allies. For example, Voss’s (2005) study of a colonial outpost in California shows that colonial residents have different identities and higher social status than other local indigenous people. A general model to summarize these case studies might be that the support of a colonial power combined with high local values for imported goods, might lead to competition among individuals. In this study, I will use this model of competition to explain the changes in social inequality at Kiwulan before and after European contact.

@@

>>>>

The burial data we analyzed in this paper are collected from the upper component of Kiwulan site, an Iron Age settlement site (AD1350-AD1950) located in northeastern Taiwan which experienced the European colonial impacts in the 17th century and the large wave of Chinese immigrants in the 19th century. The excavation revealed abundant pottery sherds, imported ceramics and stonewares, wooden artifacts, stone tools, metal artifacts, imported glass beads and agates beads, and pipes [@Chen2007]. In addition to these artifacts, 90 burials, hundreds of middens, storage pits, and postholes with in-situ posts were also excavated. The burials were mostly located in the AD section, which is the largest open area at Kiwulan site that provides continuous stratigraphic sections suitable for comparison. Those burials are oriented in an east-west direction located on the north side of the house structures indicated by postholes and in-situ wooden posts. Previous research indicates the presence of economic inequality between burials, but there is debate about whether these represent an egalitarian or stratified society [@Cheng2008; @Hsieh2012]. @Cheng2008 interprets the unequal distribution of prestige materials, such as the golden beads, between burials, as evidence for hierarchy. However, @Hsieh2012 suggests a relatively egalitarian form from the comparative analysis of frequency and proportion of burial goods. She finds that the rich burials were usually associated with elders, which might indicate achieved, rather than inherited, status. The use of prestige goods in burials might be traced back before the European arrival according to historical records from Spanish and Chinese [@Borao2009; @LiandWu2006). Analysing burial data will give an insight into the social reactions of Kiwulan residents and provide a way to examine and explain the changes in social inequality at Kiwulan before and after European contact.

@@

The archaeological sites in northeastern Taiwan show some evidence of accumulation of imported prestige goods in burials [@Cheng2008], which might indicate the pursuit of prestige or wealth. In addition to prestige, European colonial powers could have provided military support to indigenous allies. For example, Voss’s (2005) study of a colonial outpost in California shows that colonial residents have different identities and higher social status than other local indigenous people. A general model to summarize these case studies might be that the support of a colonial power combined with high local values for imported goods, might lead to competition among individuals. In this study, I will use this model of competition to explain the changes in social inequality at Kiwulan before and after European contact.

@@

Figure shows the Bayesian goodness of fit diagnostics plots where the red lines represent the distributions of the observed data and the box plots represent the GOF distributions of 10000 network graphs simulated from ERGMs based on the estimated posterior distribution. The grey lines mark the 95% intervals. X-axis means the proportion of nodes
